Layered Grammar for Alluvial Plots

### 2020-01-06 paper.rmd
improvements + alternatives to splines

While questions and requests by users have prompted many improvements, the current version is feature complete with one exception: Alternative flow elements will be implemented and controlled by a new parameter. The current splines will remain the default.

>>>>

While questions and requests by users have prompted many improvements, the current version is feature complete with one exception: improvements and alternatives to the flow elements connecting lodes. The current splines will remain the default.
